Servis: A dependently typed DSL for web APIs

### 2016-08-25 paper/paper.tex
Final final draft

TODO reword
\begin{itemize}
  \item We point out several problems and limitations of the original Servant DSL
  \item We show a port of servant to Idris, a dependently-typed language
  \item We show how new techniques from Idris can help mitigate some of the problems that Servant has.
\end{itemize}

@@

% TODO add text
\begin{minted}{idris}
( HasDocs capture
, HasDocs query
, HasDocs req
, HasDocs resp
) => HasDocs (API capture query req resp) where
  docs (OneOf (x::[])) = docs x
  docs (OneOf (x::y::xs)) = docs x ++ "\n" ++ oneOf (y::xs)
\end{minted}

@@

\begin{minted}{idris}
Application : Type
Application = (url : URL) -> (requestBody : Maybe String) -> IO String
\end{minted}
% TODO reword a bit

@@

We can use the same technique for encoding responses:
\begin{minted}{idris}
interface Universe u => ToResponse u where
  toResponse : (v : u) -> el v -> String
\end{minted}
% TODO reword
% TODO CHECKED UNTIL HERE. PAGE 11
For example, we could use this to encode values in the \mintinline{idris}{ReqResUniverse} universe from
Listing~\ref{code:api}:
\begin{minted}{idris}
  ToResponse ReqResUniverse where
    toResponse USER (MkUser id name email password) =
      "MkUser " ++ show id ++ " " ++ show name
    toResponse (LIST elem) xs =
      foldr (++) ""  . map (toResponse elem) $ xs
\end{minted}

>>>>

\begin{itemize}
  \item We point out several problems and limitations of the original Servant DSL
  \item We show a port of Servant to Idris, a dependently-typed language
  \item We show that Idris gives us new techniques to tackle these identified problems
\end{itemize}

@@

\begin{minted}{idris}
( HasDocs capture
, HasDocs query
, HasDocs req
, HasDocs resp
) => HasDocs (API capture query req resp) where
  docs (OneOf (x::[])) = docs x
  docs (OneOf (x::y::xs)) = docs x ++ "\n" ++ oneOf (y::xs)
\end{minted}

@@

\begin{minted}{idris}
Application : Type
Application = (url : URL) -> (requestBody : Maybe String) -> IO String
\end{minted}

@@

We can use the same technique for encoding responses:
\begin{minted}{idris}
interface Universe u => ToResponse u where
  toResponse : (v : u) -> el v -> String
\end{minted}
We could use this to encode values in the \mintinline{idris}{ReqResUniverse} universe from
Listing~\ref{code:api}:
\begin{minted}{idris}
  ToResponse ReqResUniverse where
    toResponse USER (MkUser id name email password) =
      "MkUser " ++ show id ++ " " ++ show name
    toResponse (LIST elem) xs =
      foldr (++) ""  . map (toResponse elem) $ xs
\end{minted}
